Transient Corotating Clumps Around Adolescent Low-Mass Stars From Four Years of TESS

### 2023-08-31 paper/ms.tex
Update ms: discussion and conclusion
Co-authored-by: Joshua Winn <jnwinn@princeton.edu>

% 250 word max!
\begin{abstract}
  We study a set of sub-solar mass pre-main-sequence stars
  with rotation periods of 0.2--2 days, optical variability amplitudes
  of a few percent, and sharp recurring light curve features that last for
  hundreds of cycles.  The sharp features are probably caused by
  eclipsing clumps of dust or gas orbiting at the corotation radius.
  We refer to this class of variable star as ``complex rotators'' (CRs).
  To improve our understanding of these
  enigmatic stars, we conducted a survey for CRs using TESS
  short-cadence data collected between 2018~July and 2022~September.
  Our search of \nstarssearched\ K and M dwarfs with $T$$<$16 and
  $d$$<$150\,pc yielded \ngoods\ high-quality CRs, most of which are
  new discoveries.  Our sample includes the brightest
  ($T$$\approx$9.5), closest ($d$$\approx$20\,pc), and oldest
  ($\approx$200\,Myr) known CRs.  One of the new discoveries, LP
  12-502, stands out for the complexity of its light curve --- with as
  many as eight flux dips per cycle --- and the detail with which the
  evolution in each dip's amplitude and phase can be tracked over
  1{,}500 cycles.  We argue that corotating gas or dust remains the
  most viable explanation for CRs. The gas or dust is probably
  entrained by the star's magnetic field, and the sharp features may
  result from a multipolar field topology, a hypothesis supported by
  correspondences between the light curves of CRs and of B stars
  known to have strong multipolar magnetic fields.
\end{abstract}

@@

		\vspace{-0.65cm}
		\subfloat{
			\includegraphics[width=0.66\textwidth]{f1b.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Complex rotators (CRs)}:
		{\it Top:} Phase-folded TESS light curves for three CRs.  Each
		panel shows the average of the data accumulated over one month,
		relative to the mean stellar brightness.
		Gray circles are raw 2-minute data; black circles are binned to
		300 points per cycle.  The period in hours is printed in the
		bottom right corner.  Left-to-right, the objects are LP 12-502
		(TIC 402980664; Sector~19), TIC 94088626 (Sector 10), and TIC
		425933644 (Sector~28).
		{\it Bottom:} Cartoon explanations for the phenomenon.  The dust
		clump scenario (left) and prominence scenario (right) both invoke
		magnetically-entrained corotating material.
	}
	\label{fig:f1}
\end{figure*}

@@

Figure~\ref{fig:f1} illustrates two proposed models for the extrinsic
material.  The first scenario invokes opaque dust ``clumps'' that
orbit near the Keplerian corotation radius [$R_{\rm c} =
(GM/\Omega^2)^{1/3}$, where $\Omega = 2\pi/P_{\rm rot}$] and
periodically transit the star
\citep{2017AJ....153..152S,2023MNRAS.518.4734S}.  The second scenario
invokes ``prominences'', long-lived condensations of cool, dense,
marginally-ionized gas that are embedded within the hotter corona and
that corotate with the star
\citep{1989MNRAS.238..657C,2019MNRAS.482.2853J,2022MNRAS.514.5465W}.
These hypothetical prominences are analogous to quiescent prominences
and filaments seen in the solar corona \citep[see
e.g.][]{2015ASSL..415.....V}, though rather than existing at a
fraction of the stellar radius as in the solar case, they would exist
at distances of a few stellar radii.  A final possibility is that an
optically-thick ring obscures a small portion of the stellar
photosphere \citep{2019ApJ...876..127Z}.  Hot spots passing behind
such a ring could produce sudden dips.  We do not favor this scenario
(see Appendix~\ref{app:ring}).

@@

In both models, the corotation radius is the location at which matter
concentrates.  The empirical basis for this is that
the sharp CR features are superposed over smooth, quasi-sinusoidal
starspot profiles.  The theoretical importance of the corotation
radius has been discussed in studies of rapid magnetic rotators
\citep[e.g.][]{1973ApJ...184..271L,1985Ap&SS.116..285N,2005ApJ...634.1214L}.
%including neutron stars \citep[e.g.]{1973ApJ...184..271L}, magnetic
%massive stars \citep[e.g.][]{1985Ap&SS.116..285N}, and accreting T
%Tauri stars \citep[e.g.][]{2005ApJ...634.1214L}.  
In regions where the
magnetic field dominates the flow (i.e.~$B^2/8\pi > \rho v^2 /2$),
matter is dragged along with the field lines.  
The tendency of both gas and dust to
become trapped at corotation is then tied to how of the four relevant
forces -- gravity, Lorentz, inertial Coriolis, and inertial
centrifugal -- the Lorentz and Coriolis only act perpendicular to
field lines, while gravity and the centrifugal force are in balance at
$R_{\rm c}$ \citep[e.g.][their Section~2]{2005MNRAS.357..251T}.  Another way to
phrase this statement is that there is a local minimum in the
effective potential of the corotating frame; given a flow from the
either the star or from a tenuous accretion disk, this local potential
minimum enables material to build up \citep{2005MNRAS.357..251T}.

@@

\begin{figure}[!t]
	\begin{center}
		\centering
		\includegraphics[width=0.46\textwidth]{f2completeness.pdf}
		\vspace{-0.2cm}
		\caption{
			{\bf Completeness of the TESS 2-minute data for late-K
      and early M dwarfs near the Sun, from Sectors 1-55.}  
      The orange dotted curve shows the number of stars in successive
      radial shells, each with a width of 10\,pc.  To be counted,
      these stars must meet the listed conditions: they must be red dwarf
      stars
      ($\bprp$>$1.5$; $M_{\rm G}$>4) amenable for TESS
      observations ($T$<16).  The blue solid curve shows the fraction
      of such stars with at least one sector of TESS 2-minute cadence
      data acquired between Sectors 1-55.
		}
			\vspace{-0.5cm}
		\label{fig:completeness}
	\end{center}
\end{figure}

@@

{\sc Dip durations}---The shortest dip duration for any of the
individual LP 12-502 dips seems to be $\approx$0.06\,$P$ $\approx$
1.08\,hr.  This is very similar to the characteristic timescale of of
transiting small body at the corotation radius,
\begin{equation}
T_{\rm dur} \equiv R_\star P_{\rm rot} / (\pi a) = 1.02\pm 0.10\,{\rm hr},
\end{equation}
where we have inserted the stellar radius and mass derived in
Section~\ref{subsec:starprops}.  Thus, the shortest-duration dips
could be produced by transits of bodies or distributions of material
that are smaller than the star.  The corotation radius corresponds to
$a/R_\star \approx 5.8$, i.e., the transit of a body at the corotation
radius has a duration about six times shorter than a feature on the
stellar photosphere that is carried across the visible hemisphere by
rotation.  On the other hand, some dip durations are sufficiently long
that an explanation involving transits would require structures that
are larger than the star along the direction of orbital motion.

@@

%FIXME TODO LEFT OFF HERE

@@

In identifying the two candidate CRs with outlying SEDs
(TICs~193136669 and TIC~57830249; Section~\ref{subsec:irexcess}), we
were prompted to reconsider our light curve-based labeling, and
ultimately concluded that these sources are dippers.  This episode
suggests that there could be overlap between CRs and dippers.  It is
also worth emphasizing that our labeling of e.g.~TIC~57830249 was
based on a single sector of TESS data (Sector~36) when its behavior
was relatively periodic and it showed dip depths of a few percent.
However, in other TESS sectors (e.g. Sector~10), this source looks
completely different, varying in apparent flux by a factor of two,
with no discernible periodicity at all.

Assessing these results against the backdrop of our increasing
understanding of dippers
\citep[e.g.][]{2014AJ....147...82C,2016ApJ...816...69A,2021ApJ...908...16R,2022ApJS..263...14C,2022MNRAS.514.1386G},
it is clear that the loss of an infrared excess is associated with
strong changes in a star's optical variability.  It is reasonable to
imagine connections between CRs and dippers: both classes of object
can show transient flux dips that are relatively narrow in duration.
The dips in both are probably associated with clumps of dust or gas.
However the CR dips are generally more periodic and less deep than
those of dippers; they also display far less transience over
timescales of a few to tens of cycles.  The CRs also have
demonstrably less dust than (most) dipper stars.  At a population
level, the CR stars are also older.  A common mystery between the
CRs and dippers, in our own estimation, is how exactly the {\it
narrowness} of the dust clumps is produced.  It is not unreasonable to
imagine a similar mechanism operating for both types of object, tied
perhaps to a shared magnetic topology, or perhaps to a preference for
dust to inspiral to the star in clumped structures.

%\subsection{Are half-cycles important?}
%
%The interval of half a cycle period could be significant in the
%context of CRs for two reasons.  The first is that for material on a
%circular orbit viewed edge-on, a half-cycle corresponds to the
%interval between transit and secondary eclipse.  The second is that
%the half-cycle also corresponds to the interval over which half of the
%star's surface is visible.  Of the CRs in Figures~\ref{fig:cqvs}
%and~\ref{fig:evoln}, a fraction that seems greater than random might
%exhibit a preference for showing dips or peaks that correspond to the
%half-cycle interval.
%
%One set of CRs shows ``CR behavior'' (some form of dip complex), but
%which only lasts for half of any given cycle.  TIC~206544316 (Sector
%2) is a canonical example; TIC~405910546 (Sector 38), TIC~167664935
%(Sector 38), TIC~146539195 (Sector 5), TIC~118449916 (Sector 44), and
%TIC~312410638 (Sector 38) seem to show the same tendency.
%
%An independent set of CRs exhibits small dips roughly half a cycle
%after large dips; it is tempting to label the small dips secondary
%eclipses.  Such sources include TIC~402980664 (Sector 25; relative to
%the sharpest, deepest minimum), TIC~89463560 (Sector 36),
%TIC~224283342 (Sector 2), and TIC~442571495 (Sector 12).  For the
%particular case of TIC~224283342, this observation, coupled with Gaia
%DR3 radial velocities suggesting a radial velocity scatter exceeding
%20\,\kms, suggests that the system could be a low-mass eclipsing
%binary transiting a giant polar spot, analogous to TOI-3884
%\citep{2022A&A...667L..11A}.
%
%In general however, it is challenging to interpret the significance of
%the potential ``half-period regularities'';  the CRs exhibit such a
%wide range of variability that for seemingly any regularity one might
%posit, it is easy to come up with counter-example objects which do not
%follow the trend.  In other words, these half-cycle CRs could simply
%be a product of the human tendency to pattern match.

@@

We can estimate the mass of a transiting cloud by first converting the
transit depth to an effective cloud radius, $R_{\rm cloud}$.  For most
CRs in Figure~\ref{fig:cqvs}, this yields $\approx$2-20\,$R_\oplus$.
A minimum constraint on the number density follows by requiring the
cloud to be optically thick.  For cases like LP 12-502, this is
reasonable because the transit duration of the shortest dips implies
$R_{\rm cloud}\ll R_\star$.  Carrying out the relevant calculation
assuming the occulting material is dust grains 1\,$\mu$m in size,
\citet{2023MNRAS.518.4734S} reported minimum cloud masses of order
$10^{12}$\,kg (their Eq.~23), which scale linearly with both the
optical depth and dust grain radius.  This is comparable to a small
asteroid; the asteroid belt itself has a mass of order
$\approx$10$^{21}$\,kg \citep{2019Icar..319..812P}.  If the material
were cool gas prominences rather than dust, the mass would need to be
of order $10^{14}$\,kg \citep{1990MNRAS.247..415C}, about 100$\times$
larger than the requisite dust mass.

Our observations provide a direct measurement of how often dips appear
and disappear, both due to sudden state-switches, and due to more
gradual, secular evolution.  For instance, LP~12-502 showed three
``state-switch'' events over the six months of available TESS
observations, during cycles 248-264, 299-315, and 1233-1247.  In each
case, a dip ``turned off''.  It is plausible to imagine that these
events correspond to either mass being ejected from the corotating
clumps, or else perhaps being accreted onto the star.  In either case,
the corresponding $\dot{M} \equiv M\cdot {\rm d}N/{\rm d}t$
time-averaged over six months is $\approx$3$\times$$10^{-18}
M_\odot\,{\rm yr}^{-1} \approx 1\times10^{-12} M_\oplus\,{\rm
yr}^{-1}$.  Considered cumulatively over the $\approx$$10^8$ years for
which the CR phenomenon is observed, this yields a cumulative moved
dust mass of $10^{-4}\,M_\oplus$, of order the Solar System's asteroid
belt.  If the occulting material is gas, the masses involved would be
of order 100 times larger.  For cases in which we observe the {\it
growth} of dips, such as the Sector~29 data for TIC~224283342, or
Sector~5 of TIC~294328885, the dip depths typically increase by of
order a few percent over ten to twenty days.  This growth rate yields
a mass flux one order of magnitude larger than the earlier estimate.

@@

An argument against the connection between CRs and the $\sigma$~Ori~E
analogs is that the light curve of $\sigma$~Ori~E is much simpler than
those in Figure~\ref{fig:cqvs}, with only two broad local minima, and
one ``hump'' (Figure~\ref{fig:bstar}; see also
\citealt{2022ApJ...924L..10J}).  Within the model proposed by
\citeauthor{2005ApJ...630L..81T}, this is explained by the simplicity
of the star's magnetic field, which is well-approximated by a dipole,
similar to most other magnetic B stars
\citep{2007A&A...475.1053A,2009ARA&A..47..333D}.  The magnetic axis
needs to be tilted relative to the stellar spin axis in order to match
the qualitative behavior of both the broadband light curves, and the
line-profile variations seen in hydrogen, helium, and carbon
\citep{2012MNRAS.419..959O}.

Two exceptions to the rule of ``simple field topologies for magnetic B
stars'' are HD~37776 and HD~64740, which are B stars that were
previously known from spectropolarimetry to have field geometries
dominated by high order multipoles \citep{2011ApJ...726...24K}.
Reviewing the literature, we learned that recent TESS light curves of
these two B stars appear surprisingly similar to the CR light curves
\citep{2020pase.conf...46M}.  The middle row of Figure~\ref{fig:bstar}
shows the phased TESS light curves for these two outlying magnetic B
stars, with by-eye ``best matching'' CRs shown underneath for comparison.  The
number of dips per cycle, the shapes of the dips, and the dip depths
relative to the sinusoidal envelope all appear to be similar.  This surprising connection 
suggests that the
highly-structured M dwarf light curves may imply multipolar magnetic
fields -- since it is the complex fields which are the defining
characteristic of these two B stars, relative to other known magnetic
B stars like $\sigma$~Ori~E.  This is consistent with the
non-axisymmetric topologies that have been reported in a small number
of M dwarfs for which Zeeman Doppler Imaging is technically feasible
\citep[see][and references therein]{2021A&ARv..29....1K}.

The physical similarity between the B stars and the M dwarfs
presumably has its origin in the existence of a ``centrifugal
magnetosphere'' \citep[see][]{2013MNRAS.429..398P}.  In other words,
both classes of objects probably satisfy the condition $R_{\rm M} >
R_{\rm c}$, for $R_{\rm M}$ the magnetospheric radius (sometimes
referred to as the Alfv\'en radius).  When this condition
holds, stable points exist wherever the outward centrifugal force is
balanced by the combined effect of gravity and magnetic tension along
closed field loops \citep{1985Ap&SS.116..285N}.  In the converse
``dynamical'' case, when  $R_{\rm M} < R_{\rm c}$, material
interior to the magnetospheric radius returns to the stellar surface
over the free-fall timescale.  A simple estimate assuming a dipole
field with $B_0\approx1\,{\rm kG}$ at the star's surface, a local
plasma number density $n\approx10^9\,{\rm cm^{-3}}$, and a plasma
temperature $10^6\,{\rm K}$ gives magnetospheric radii of order a few
times the corotation radii, $R_{\rm c}$.  This suggests that the
existence of a centrifugal magnetosphere is plausible in young,
rapidly rotating M dwarfs.

% NOTE to the arxiv crawlers:

% While there are some qualitative connections to Jupiter-Io, it's not
% perfect.  In that system, R_A>R_cr...  But the plasma torus exists
% near Io's 42 hour orbit ...and is nonetheless STILL FORCED into
% corotation at a 10hr period (presumably by Jupiter's B-field).  This
% type of structure is very different, because here we actually see
% the plasma at corotation!

@@

In our target sample, we found \ngoods\ objects that showed complex
quasiperiodic behavior over at least one TESS sector.  These \ngoods\
bona fide CRs are listed in Table~\ref{tab:thetable}.  This table also
includes an additional \nmaybes\ ambiguous CRs, whose designation is
less certain, and \ndebunked\ impostors.  We inferred ages for all but
two of the \nallcands\ objects based on association memberships; we
also derived temperatures and radii using SED fitting, and then
inferred stellar masses by interpolating against stellar evolutionary
models.  We caution that our selection function was not
volume-limited: the TESS 120-second stellar sample had a heterogeneous
selection function which may have been biased in favor of young stars
over field stars.  Previous work however has shown that $\approx$1-3\%
of M dwarfs younger than $\approx$100\,Myr show the CR phenomenon
\citep{2016AJ....152..114R,2022AJ....163..144G}.

@@

Figures~\ref{fig:tic3006timegroups} and~\ref{fig:tic3006river} show
120-second cadence data for TIC~300651846, a CR in the TESS
continuous viewing zone.  If it were not for the existence of
TIC~402980664, this source would probably have received greater
attention.  With the exception of a few sectors, TESS data will exist
for TIC~300651846 for at least Sectors 1-12, 27-39, and 61-69.  While
most of the available data exist in the full frame images,
Figures~\ref{fig:tic3006timegroups} and~\ref{fig:tic3006river} focus
only on the currently available 120-second cadence data.

>>>>

% 250 word max!
\begin{abstract}
  We study a set of pre-main-sequence stars
  with sub-solar masses, rotation periods of 0.2--2 days, optical variability amplitudes
  of a few percent, and sharp recurring light curve features that last for
  hundreds of cycles.  The sharp features are probably caused by
  eclipsing clumps of dust or gas orbiting at the corotation radius.
  We refer to this class of variable star as ``complex rotators'' (CRs).
  To improve our understanding of these
  enigmatic objects, we conducted a survey for CRs using TESS
  short-cadence data collected between 2018~July and 2022~September.
  Our search of \nstarssearched\ K and M dwarfs with $T$$<$16 and
  $d$$<$150\,pc yielded \ngoods\ high-quality CRs, most of which are
  new discoveries.  Our sample includes the brightest
  ($T$$\approx$9.5), closest ($d$$\approx$20\,pc), and oldest
  ($\approx$200\,Myr) known CRs.  One of the new discoveries, LP
  12-502, stands out for the complexity of its light curve --- with as
  many as eight flux dips per cycle --- and the detail with which the
  evolution in each dip's amplitude and phase can be tracked over
  1{,}500 cycles.  We argue that corotating gas or dust remains the
  most viable explanation for CRs. The gas or dust is probably
  entrained by the star's magnetic field, and the sharp features may
  result from a multipolar field topology, a hypothesis supported by
  correspondences between the light curves of CRs and of B stars
  known to have strong multipolar magnetic fields.
\end{abstract}

@@

		\vspace{-0.65cm}
		\subfloat{
			\includegraphics[width=0.66\textwidth]{f1b.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Complex rotators (CRs)}:
		{\it Top:} Phase-folded TESS light curves for three CRs.  Each
		panel shows the average of the data accumulated over one month,
		relative to the mean stellar brightness.
		Gray circles are raw 2-minute data; black circles are binned to
		300 points per cycle.  The period in hours is printed in the
		bottom right corner.  Left-to-right, the objects are LP 12-502
		(TIC 402980664; Sector~19), TIC 94088626 (Sector 10), and TIC
		425933644 (Sector~28).
		{\it Bottom:} Cartoon explanations for the phenomenon.  The dust
		clump scenario (left) and gas prominence scenario (right) both invoke
		magnetically-entrained corotating material.
	}
	\label{fig:f1}
\end{figure*}

@@

Figure~\ref{fig:f1} illustrates two proposed models for the extrinsic
material.  The first scenario invokes opaque dust ``clumps'' that
orbit near the Keplerian corotation radius [$R_{\rm c} =
(GM/\Omega^2)^{1/3}$, where $\Omega = 2\pi/P_{\rm rot}$] and
periodically transit the star
\citep{2017AJ....153..152S,2023MNRAS.518.4734S}.  The second scenario
invokes ``prominences'', long-lived condensations of cool, dense,
marginally-ionized gas that are embedded within the hotter corona and
that corotate with the star
\citep{1989MNRAS.238..657C,2019MNRAS.482.2853J,2022MNRAS.514.5465W}.
These hypothetical prominences are analogous to quiescent prominences
and filaments seen in the solar corona \citep[see
e.g.][]{2015ASSL..415.....V}, though rather than existing at a
fraction of the stellar radius as in the solar case, they would exist
at distances of a few stellar radii.  A final possibility is that an
optically-thick ring obscures a narrow band of the stellar
photosphere \citep{2019ApJ...876..127Z}.  Hot spots passing behind
such a ring could produce sudden dips.  We do not favor this scenario
(see Appendix~\ref{app:ring}).

@@

In both models, the corotation radius is the location at which matter
concentrates.  The empirical basis for this is that
the sharp CR features are superposed over smooth, quasi-sinusoidal
starspot profiles.  The theoretical importance of the corotation
radius has been discussed in studies of magnetic rotators
\citep[e.g.][]{1973ApJ...184..271L,1985Ap&SS.116..285N,2005ApJ...634.1214L}.
%
%including neutron stars \citep[e.g.]{1973ApJ...184..271L}, magnetic
%massive stars \citep[e.g.][]{1985Ap&SS.116..285N}, and accreting T
%Tauri stars \citep[e.g.][]{2005ApJ...634.1214L}.  
%
In regions where the magnetic field dominates the flow (i.e.~$B^2/8\pi
> \rho v^2 /2$), matter is dragged along with the field lines.  The
tendency for charged gas or dust to become trapped at corotation is
then tied to how of the four relevant forces -- gravity, Lorentz,
inertial Coriolis, and inertial centrifugal -- the Lorentz and
Coriolis only act perpendicular to field lines, while gravity and the
centrifugal force are in balance at $R_{\rm c}$ \citep[e.g.][their
Section~2]{2005MNRAS.357..251T}.  Another way to phrase this statement
is that there is a local minimum in the effective potential of the
corotating frame; given a flow from the either the star or from a
tenuous accretion disk, this local potential minimum enables material
to build up \citep{2005MNRAS.357..251T}.

@@

\begin{figure}[!t]
	\begin{center}
		\centering
		\includegraphics[width=0.43\textwidth]{f2completeness.pdf}
		\vspace{-0.2cm}
		\caption{
			{\bf Completeness of the TESS 2-minute data for late-K
      and early M dwarfs near the Sun, from Sectors 1-55.}  
      The orange dotted curve shows the number of stars in successive
      radial shells, each with a width of 10\,pc.  To be part of our selection function,
      these stars must meet the listed conditions: they must be red dwarf
      stars
      ($\bprp$>$1.5$; $M_{\rm G}$>4) amenable for TESS
      observations ($T$<16).  The blue solid curve shows the fraction
      of such stars with at least one sector of TESS 2-minute cadence
      data acquired between Sectors 1-55.
		}
			\vspace{-0.5cm}
		\label{fig:completeness}
	\end{center}
\end{figure}

@@

{\sc Dip durations}---The shortest dip duration for any of the
individual LP 12-502 dips seems to be $\approx$0.06\,$P$ $\approx$
1.08\,hr.  This is very similar to the characteristic timescale of a
transiting small body at the corotation radius,
\begin{equation}
T_{\rm dur} \equiv R_\star P_{\rm rot} / (\pi a) = 1.02\pm 0.10\,{\rm hr},
\end{equation}
where we have inserted the stellar radius and mass derived in
Section~\ref{subsec:starprops}.  Thus, the shortest-duration dips
could be produced by transits of bodies or distributions of material
that are smaller than the star.  The corotation radius corresponds to
$a/R_\star \approx 5.8$, i.e., the transit of a body at the corotation
radius has a duration about six times shorter than a feature on the
stellar photosphere that is carried across the visible hemisphere by
rotation.  On the other hand, some dip durations are sufficiently long
that an explanation involving transits would require structures that
are larger than the star along the direction of orbital motion.

@@

@@

About one in three young stars with infrared-detected inner dusty
disks show quasiperiodic or stochastic dimming over timescales of
roughly one day \citep[e.g.][]{2010A&A...519A..88A}.  The dimming
amplitudes can reach a few tenths of the stellar brightness, and dips
with identical depths and phases rarely recur.  These ``dipper'' stars
are probably explained by occulting circumstellar dust in the inner
disk
\citep[e.g.][]{2014AJ....147...82C,2016ApJ...816...69A,2021ApJ...908...16R,2022ApJS..263...14C}.
While the phenomenon can persist beyond $\approx$10\,Myr
\citep{2019MNRAS.488.4465G,2022MNRAS.514.1386G}, in all such cases it
seems to be associated with the presence of infrared excesses.
Phenomenologically, dippers are different from CRs in that their dips
are usually deeper, less periodic, and more variable in depth over
timescales of only one or a few cycles.  Dipper stars also tend to be
younger, since they tend to be classical T Tauri stars with infrared
excesses.

In identifying the two candidate CRs with outlying SEDs
(TICs~193136669 and TIC~57830249; Section~\ref{subsec:irexcess}), we
were prompted to reconsider our light curve-based labeling, and
ultimately concluded that these sources are dippers.  This episode
suggests that there could be overlap between CRs and dippers.  Taking
TIC~57830249 as one example, the Sector~36 TESS data are suggestive of
a CR, with relatively periodic, sharp dips with depths of a few
percent.  The Sector~10 data are completely different, varying in
apparent flux by a factor of two, with no discernible periodicity at
all.  Perhaps this source becomes a ``dipper'' when an inflow of dust
reaches the inner disk wall, and is otherwise a ``CR'' when the inner
disk is starved of dust.

Although this outlier is intriguing, stars without infrared excessess
typically have more stable optical light curves than those with
infrared excesses.  While some dippers may evolve into CRs after the
disk is mostly gone, this would be generically expected based on the
population statistics: young stars become older.  There may be no
other causal connection between the two evolutionary stages.  With
that said, a common mystery between the CRs and dippers is how exactly
the {\it narrowness} of the dust-induced dimmings is produced.  It is
not unreasonable to imagine a similar mechanism operating for both
types of object, tied perhaps to a shared magnetic topology, or
perhaps to a preference for dust to inspiral to the star in clumped
structures.

%\subsection{Are half-cycles important?}
%
% NOTE to arxis readers: the answer was: "maybe in a few cases, but
% this manuscript was already too long!".
%
%The interval of half a cycle period could be significant in the
%context of CRs for two reasons.  The first is that for material on a
%circular orbit viewed edge-on, a half-cycle corresponds to the
%interval between transit and secondary eclipse.  The second is that
%the half-cycle also corresponds to the interval over which half of the
%star's surface is visible.  Of the CRs in Figures~\ref{fig:cqvs}
%and~\ref{fig:evoln}, a fraction that seems greater than random might
%exhibit a preference for showing dips or peaks that correspond to the
%half-cycle interval.
%
%One set of CRs shows ``CR behavior'' (some form of dip complex), but
%which only lasts for half of any given cycle.  TIC~206544316 (Sector
%2) is a canonical example; TIC~405910546 (Sector 38), TIC~167664935
%(Sector 38), TIC~146539195 (Sector 5), TIC~118449916 (Sector 44), and
%TIC~312410638 (Sector 38) seem to show the same tendency.
%
%An independent set of CRs exhibits small dips roughly half a cycle
%after large dips; it is tempting to label the small dips secondary
%eclipses.  Such sources include TIC~402980664 (Sector 25; relative to
%the sharpest, deepest minimum), TIC~89463560 (Sector 36),
%TIC~224283342 (Sector 2), and TIC~442571495 (Sector 12).  For the
%particular case of TIC~224283342, this observation, coupled with Gaia
%DR3 radial velocities suggesting a radial velocity scatter exceeding
%20\,\kms, suggests that the system could be a low-mass eclipsing
%binary transiting a giant polar spot, analogous to TOI-3884
%\citep{2022A&A...667L..11A}.
%
%In general however, it is challenging to interpret the significance of
%the potential ``half-period regularities'';  the CRs exhibit such a
%wide range of variability that for seemingly any regularity one might
%posit, it is easy to come up with counter-example objects which do not
%follow the trend.  In other words, these half-cycle CRs could simply
%be a product of the human tendency to pattern match.

@@

Assuming for the moment that the obscuring material is dust, we can
estimate the mass of a transiting clump. First, we convert the transit
depth into an effective cloud radius, $R_{\rm cloud}$.  For most CRs
in Figure~\ref{fig:cqvs}, this yields $\approx$2-20\,$R_\oplus$.  A
minimum constraint on the number density of dust particles is obtained
by requiring the cloud to be optically thick.  For cases like LP
12-502, this is reasonable because the transit duration of the
shortest dips implies $R_{\rm cloud}\ll R_\star$.  Carrying out the
relevant calculation assuming the dust grains are 1\,$\mu$m in size,
\citet{2023MNRAS.518.4734S} reported minimum cloud masses of order
$10^{12}$\,kg (their Eq.~23), which scale linearly with both the
optical depth and dust grain radius.  This is comparable to a small
asteroid; the asteroid belt itself has a mass of order
$\approx$10$^{21}$\,kg \citep{2019Icar..319..812P}.  A similar
calculation that assumed occulting clupms of hydrogen, rather than
dust, derived gas prominence masses of at least $10^{14}$\,kg
\citep{1990MNRAS.247..415C}, about 100$\times$ larger than the lower
limit on the dust mass.

If the disappearance of a dip represents the permanent loss of the
obscuring material -- for example, if it is the result of a dust clump
being accreted or ejected -- then we can also estimate the rate at
which mass is flowing through the structures that lead to dips.  For
instance, LP~12-502 showed three ``state-switch'' events over the six
months of available TESS observations, during cycles 261, 309, and
1241 (Figure~\ref{fig:lpriver0}).  The other source for which we
performed a comparable analysis, TIC~300651846
(Appendix~\ref{app:tic3006}), showed two state-switches over 11
months.  In all such cases, at least one dip turned off.  For purposes
of estimation, we will take LP 12-502 as our prototype.  Assuming the
occulting material is dust, the corresponding $\dot{M} \equiv M\cdot
{\rm d}N/{\rm d}t$ time-averaged over six months is
$\approx$3$\times$$10^{-18} M_\odot\,{\rm yr}^{-1} \approx
1\times10^{-12} M_\oplus\,{\rm yr}^{-1}$.  Considered cumulatively
over the $\approx$$10^8$ years for which the CR phenomenon is
observed, this yields a cumulative moved dust mass of
$10^{-4}\,M_\oplus$, of order the Solar System's asteroid belt.  If
the occulting material is gas, the masses involved would be of order
100 times larger.  For cases in which we observe the {\it growth} of
dips, such as the Sector~29 data for TIC~224283342, or Sector~5 of
TIC~294328885, the dip depths typically increase by of order a few
percent over ten to twenty days.  This growth rate yields a mass flux
one order of magnitude larger than the earlier estimate.

@@

An argument against the connection between CRs and the $\sigma$~Ori~E
analogs is that the light curve of $\sigma$~Ori~E is simpler than
those in Figure~\ref{fig:cqvs}, with only two broad local minima, and
one ``hump'' (Figure~\ref{fig:bstar}; see also
\citealt{2022ApJ...924L..10J}).  Within the model proposed by
\citeauthor{2005ApJ...630L..81T}, the simplicity of the light curve is
the result of a simple dipolar magnetic field, which is typical of
magnetic B stars \citep{2007A&A...475.1053A,2009ARA&A..47..333D}.  The
magnetic axis needs to be tilted relative to the stellar spin axis in
order to match the qualitative behavior of both the broadband light
curves, and the line-profile variations seen in hydrogen, helium, and
carbon \citep{2012MNRAS.419..959O}.

Two interesting and possibly telling exceptions to the rule that
magnetic B stars have simple light curves are HD~37776 and HD~64740.
Both stars are known from spectropolarimetry to have field geometries
dominated by high order multipoles \citep{2011ApJ...726...24K}.
And, recent TESS light curves of these two B stars appear surprisingly
similar to the CR light curves \citep{2020pase.conf...46M}.  The
middle row of Figure~\ref{fig:bstar} shows the phased TESS light
curves for these two stars, with by-eye best-matching CRs shown
underneath for comparison.  The number of dips per cycle, the shapes
of the dips, and the dip depths relative to the sinusoidal envelope
are all similar.  This connection suggests that the highly structured
light curves of both the M dwarfs and the B stars are associated with
(and perhaps caused by) strong non-dipolar magnetic fields.
Non-dipolar fields for M dwarfs are plausible, given that Zeeman
Doppler Imaging has revealed non-axisymmetric magnetic field patterns
for the few M dwarfs for which this technique is technically feasible
\citep[see][and references therein]{2021A&ARv..29....1K}.

The physical similarity between the B stars and the M dwarfs
presumably has its origin in the existence of a ``centrifugal
magnetosphere'' \citep[see][]{2013MNRAS.429..398P}.  In other words,
both classes of objects probably satisfy the condition $R_{\rm m} >
R_{\rm c}$, for $R_{\rm m}$ the magnetosphere radius (sometimes called
the Alfv\'en radius).  Provided that charged particles are confined to
move along magnetic field lines, stable points that balance the
centrifugal force and gravity can then exist at the corotation radius
\citep[e.g.][]{2005MNRAS.357..251T}.  In the converse ``dynamical''
case, when $R_{\rm m} < R_{\rm c}$, material interior to the
magnetospheric radius returns to the stellar surface over the
free-fall timescale.  A simple estimate assuming a dipole field with
$B_0\approx1\,{\rm kG}$ at the star's surface, a local plasma number
density $n\approx10^9\,{\rm cm^{-3}}$, and a plasma temperature
$10^6\,{\rm K}$ gives magnetospheric radii of order a few times the
corotation radii, $R_{\rm c}$.  This suggests that the existence of a
centrifugal magnetosphere is plausible for young, rapidly rotating M
dwarfs.

% NOTE to the arxiv crawlers:
%
% While there are some qualitative connections to Jupiter-Io, it's not
% perfect.  In that system, R_m>R_c...  But the plasma torus exists
% near Io's 42 hour orbit ...and is nonetheless STILL FORCED into
% corotation at a 10hr period (presumably by Jupiter's B-field).  This
% type of structure is very different, because here we actually see
% the plasma at the corotation radius itself!

@@

In our target sample, we found \ngoods\ objects that showed complex
quasiperiodic behavior over at least one TESS sector.  These \ngoods\
bona fide CRs are listed in Table~\ref{tab:thetable}.  This table also
includes \nmaybes\ ambiguous CRs, whose designation is
less certain, and \ndebunked\ impostors.  We inferred ages for all but
two of the \nallcands\ objects based on memberships in young stellar assocations; we
also derived temperatures and radii using SED fitting, and 
inferred stellar masses by interpolating against stellar evolutionary
models.  We caution that our sample is far from being
volume-limited and is not even magnitude-limited:
the TESS 120-second stellar sample had a heterogeneous
selection function which may have been biased in favor of young stars
over field stars.  Previous work however has shown that $\approx$1-3\%
of M dwarfs younger than $\approx$100\,Myr show the CR phenomenon
\citep{2016AJ....152..114R,2022AJ....163..144G}.

@@

Figures~\ref{fig:tic3006timegroups} and~\ref{fig:tic3006river} show
120-second cadence data for TIC~300651846, a CR in the TESS
continuous viewing zone.  If it were not for the existence of
TIC~402980664, this source would have received greater
attention.  With the exception of a few sectors, TESS data will exist
for TIC~300651846 for at least Sectors 1-12, 27-39, and 61-69.  While
most of the available data exist in the full frame images,
Figures~\ref{fig:tic3006timegroups} and~\ref{fig:tic3006river} focus
only on the currently available 120-second cadence data.

During Sectors 32-39, the source shows between one and four local
minima per cycle.  During the early portions of Sectors 61-65, it is
more complex, with at least five clear local minima per
cycle.  As the source evolves, its shape becomes simpler, and the
sharpness of one global minimum appears to increase.
